Making Sequential Programs Deterministic

### 2019-03-28 experiments.tex

\section{Evaluation}
\subsection{NONDEX case study}
\begin{table}[]
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        Benchmark & Recall? & Error message source & # annotations & Type of annotation added & Comments \\ \hline
        P1 &  &  &  &  &  \\
        P2 &  &  &  &  &  \\
        P3 &  &  &  &  &  \\ 
        P4 &  &  &  &  &  \\ 
        P5 &  &  &  &  &  \\ 
        P5 &  &  &  &  &  \\ 
        P6 &  &  &  &  &  \\ 
        P6 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\ 
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P9 &  &  &  &  &  \\
        P10 &  &  &  &  &  \\
        P10 &  &  &  &  &  \\
        P11 &  &  &  &  &  \\
        P12 &  &  &  &  &  \\
        P13 &  &  &  &  &  \\
        P14 &  &  &  &  &  \\
        P15 &  &  &  &  &  \\
        P15 &  &  &  &  &  \\
        P16 &  &  &  &  &  \\
        P17 &  &  &  &  &  \\
        P18 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P20 &  &  &  &  &  \\
        P20 &  &  &  &  &  \\
        P21 &  &  &  &  &  \\
        P21 &  &  &  &  &  \\ \hline
    \end{tabular}
\end{table}

>>>>

\section{Evaluation}
\subsection{NONDEX case study}
\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{3cm}|p{2cm}|p{2cm}|p{3cm}|}
        \hline
        Benchmark & Recall? & Error message source & \#annotations & Type of annotation added & Error msg \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] &  &  &  assignment type incompatible \\
        P2 &  &  &  &  &  \\
        P3 &  &  &  &  &  \\ 
        P4 &  &  &  &  &  \\ 
        P5 &  &  &  &  &  \\ 
        P5 &  &  &  &  &  \\ 
        P6 &  &  &  &  &  \\ 
        P6 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\ 
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P9 &  &  &  &  &  \\
        P10 &  &  &  &  &  \\
        P10 &  &  &  &  &  \\
        P11 &  &  &  &  &  \\
        P12 &  &  &  &  &  \\
        P13 &  &  &  &  &  \\
        P14 &  &  &  &  &  \\
        P15 &  &  &  &  &  \\
        P15 &  &  &  &  &  \\
        P16 &  &  &  &  &  \\
        P17 &  &  &  &  &  \\
        P18 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P20 &  &  &  &  &  \\
        P20 &  &  &  &  &  \\
        P21 &  &  &  &  &  \\
        P21 &  &  &  &  &  \\ \hline
    \end{tabular}
\end{table}
